\textbf{CSDS 440 Class Project: \\Adversarial Machine Learning}

### 2020-12-05 report/article.tex

\subsection{David Meshnick's Individual Report}

@@

David please explain a bit on DeepFool as why it perturbed a huge amount while performed not so well, and maybe also why its $L_\infty$ is a lot higher than $L_2$.

@@

\ilc{DeepFool} and \ilc{D-DeepFool} have shown very similar performance across this section of experiments and their performance are considerably lacking both in terms of \textit{adversarial acc} and \textit{perturbation budget}. David, please again summarize a bit here.

@@

However, it remainds unknow why \ilc{D-DeepFool} has a much lesser \textit{benign flag} and \textit{adversarial flag} in comparision to \ilc{DeepFool}. David please have some input here thanks.

>>>>

\subsection{David Meshnick's Individual Report}
\subfile{individual_reports/dcm101}

@@

An unexpected observation came from the \ilc{DeepFool} algorithm, which iterated through more perturbations than we had anticipated. This came about as a result of DeepFool's deceptively simple nature, as it is effectively a greedy search algorithm. While the function's goal is to enact the fewest possible perturbations to confidently disrupt a classifier, its descent along its gradient does not share the same efficiency. The base learning rate ended up costing a significant amount of computational resources. However, the extension David created may be a possible solution to this problem. As elaborated upon in the individual report, the \ilc{Dynamic DeepFool} implements a logarithmically decreasing learning rate, which improves the speed at which the algorithm approaches the class label boundary. This allowed it to have a noticeably smaller quantity of perturbation iterations, and also out performing the original DeepFool in terms of attack effectiveness on an undefended learning system.

@@

\ilc{DeepFool} and \ilc{D-DeepFool} have shown very similar performance across this section of experiments and their performance are considerably lacking both in terms of \textit{adversarial acc} and \textit{perturbation budget}. However, the relative-simplicity of the algorithm lends itself more easily to modification, as demonstrated by the performance gains of simply altering the learning rate of the methods gradient traversal.

One last interesting point of comparison lies between white-box algorithms like \ilc{DeepFool} and black-box algorithms like \ilc{One Pixel Attack}. The white-box attack method had unrestrained access to the inner parameters of the victim classifier, and was typically highly effective. Meanwhile, the black-box attack could only view the inputs and outputs of the victim model, and was not as effective. However, the black-box algorithm was less computationally expensive, as well as requiring fewer parameters to act. Thus, we believe that further analysis is warranted to explore the trade-offs with regards to metrics such as computational resources and speed, between each method.

@@
